How strong is the linear relationship between the age of a driver and the distance the driver can see? If we had to guess, we might think that the relationship is negative ¡X as age increases, the distance decreases. A research firm collected data on a sample of n = 30 drivers (¡§age_distance.txt¡¨).

#load data

```{r}
library(ggplot2)
library(dplyr)

Age <- unlist(age_distance[1], use.names=FALSE)
Distance <-unlist(age_distance[2], use.names=FALSE)
```
a.	Please draw stem-leaf plots for ¡§Age¡¨ and ¡§Distance¡¨ respectively. Comments on the two plots

stem-leaf plots for ¡§Age¡¨
```{r}
stem(Age)
```
stem-leaf plots for ¡§Distance¡¨
```{r}
stem(Distance)
```

b.	Please draw a scatterplot of ¡§Age¡¨ (X ¶b) and ¡§Distance¡¨ (Y ¶b). Comments on the plot. Are there any outliers or influential observations?
```{r}
plot(Age,Distance,main="scatterplot of Age and Distance")

```
```{r}
ggplot(age_distance,aes(x=Age,y=Distance))+
  geom_point() #actual points 
```

c.	For each variable, compute the mean and standard deviation. Then compute the Pearson correlation coefficient. 
```{r}
cat("Age¡Gmean",mean(Age),"Sd",sd(Age))
```
```{r}
cat("Distance¡Gmean",mean(Distance),"Sd",sd(Distance))
```
Pearson correlation coefficient
```{r}
cor(age_distance)
```
d.	Fit the following linear regression: 
```{r}
model <- lm(Distance ~ Age,data=age_distance)
summary(model)
```
```{r}
sigma(model)**2
```

```{r}
model
```

e.	Draw the residual plot and comment on the plot.
https://www.r-bloggers.com/visualising-residuals/

```{r}
plot(model)
```
```{r}
age_distance$predicted <- predict(model)
age_distance$residuals <- residuals(model)
age_distance %>% select(Distance,predicted,residuals) %>% head()
```

```{r}
ggplot(age_distance,aes(x=Age,y=Distance))+
  geom_smooth(method = "lm", se = FALSE, color = "lightgrey") +  # Plot regression slope
  geom_segment(aes(xend = Age, yend = predicted)) +
  geom_point() + #actual points
  geom_point(aes(y=predicted),shape=1) #predicted value
```
```{r}
model.res=resid(model)
plot(age_distance$Age ,model.res,
     ylab = "Residuals",xlab = "Age",
     main = "Residual Plot")
```

f.	Draw the normal probability plot. Commet on the plot. 
https://www.surfacewalker.com/single-post/2017/03/22/R-language-%E5%B8%B8%E6%85%8BQ-Q%E5%9C%96normal-Q-Q-plot%E7%B0%A1%E4%BB%8B%E8%88%87%E7%B9%AA%E8%A3%BD
```{r}
curve(dnorm(x),from = -3.5, to = 3.5, ylab="p.d.f", main="normal distribution plot - n(0.1)")
```

g.	What is the value of R^2 ? What does this value mean? 
```{r}
r_sq <- summary(model)$r.squared
adj_r_sq <- summary(model)$adj.r.squared
cat(r_sq,adj_r_sq)
```

